\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{amsmath,amssymb}
\usepackage{enumitem}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0.75em}

\begin{document}

\begin{center}
{\Large \textbf{Referee Report}}\\[0.5em]
\textit{Computational resolution limits for super-resolution of positive sources}
\end{center}

This paper studies computational resolution limits for super-resolution of positive sources from
noisy band-limited Fourier data. The central quantitative question is how small the minimum
separation may be, as a function of the cutoff frequency $\Omega$, the noise level $\sigma$,
the minimum source amplitude $m_{\min}$, and the number of sources $n$, while still allowing
stable detection of the correct number of sources or stable recovery of their locations.
In one dimension, the paper defines the corresponding positive-source resolution limits for a
single cluster of sources, proves lower bounds with explicit constants, and combines them
with upper bounds from the authors' earlier papers. It then extends the same clustered setting
to higher dimensions.

In my view, the main contribution of the paper is Theorem~2.2, namely the lower bound for the
number-detection problem in the positive-source case. More precisely, Theorem~2.2 constructs an
$n$-point positive measure and an $(n-1)$-point positive measure whose Fourier measurements
differ by less than $2\sigma$ and whose minimum separation is
\[
\frac{2e^{-1}}{\Omega}\left(\frac{2\sigma}{m_{\min}}\right)^{\!1/(2n-2)}.
\]
This is the theorem that carries the main novelty of the paper. The result is useful because it
shows that positivity does not improve the asymptotic SRF--SNR law for number detection: the
exponent remains the same as in the general-source case. What positivity does provide is better
constants. While one may be able to adapt previously published techniques to the positive case,
this does not seem to yield explicit constants of comparable sharpness to the current work.

The support-recovery lower bound, the multidimensional extension, the instability examples, and
the numerical phase-transition sections are useful complements. They strengthen the paper and make
the overall picture more complete, but I would still regard the main new point as the
positive-source lower bound for number detection.

At the level of proof, the lower-bound argument is based on the framework developed earlier in
[32]. The main ingredients are the same: one constructs an underdetermined Vandermonde system,
exploits vanishing moments, controls the coefficients via inverse-Vandermonde/Lagrange formulas,
and bounds the remainder of the power-series expansion of $F[\gamma]$ using
factorial/Stirling estimates. The new ingredient is the additional analysis needed to enforce
positivity, especially the sign pattern that allows the null vector to be split into two positive
measures. I therefore view the argument as a nontrivial positivity-adapted refinement of [32],
rather than as a completely different method. This does not diminish the value of the result, but
it should be described accurately in the paper.

I do, however, have two main reservations that should be addressed before I can recommend
acceptance. First, the paper should state much more explicitly that the principal novelty,
relative to the previous papers, is the lower bound for number detection in the positive case.
Second, the geometric scope of the paper should be stated much more clearly. The introduction and
Section~1.2 are written broadly enough that a reader could reasonably come away with the
impression that the paper addresses positive-source super-resolution in fairly general geometry,
whereas Section~2 explicitly says that it treats the case where the point sources are tightly
spaced and form a single cluster, and Section~3 makes the analogous clustered assumption in the
multi-dimensional setting.

\textbf{Recommendation:} \emph{Accept subject to revision.}

\textbf{Comments to the authors}

\begin{enumerate}[leftmargin=2.2em]
\item \textbf{State the main novelty more clearly in the introduction and in Section~1.2.}
The sentence on p.~5 beginning ``The main contribution of this paper is quantitative
characterizations ...'' should be sharpened. In my opinion, the main new result is more specific:
it is the lower bound for the number-detection problem for positive sources, namely
Theorem~2.2. The one-dimensional upper bounds are taken from earlier papers of the authors, and
the support-recovery lower bound and multidimensional extension are useful complements. I suggest
stating this explicitly.

\item \textbf{State the single-cluster restriction much more clearly in the abstract,
introduction, and Section~1.2.}
On p.~6, Section~2 explicitly says that it considers the case where the point sources are tightly
spaced and form a cluster, and then assumes $y_j\in I(n,\Omega)$. In Section~3, the
multi-dimensional extension likewise assumes that all source locations belong to
$B_{(n-1)\pi/(2\Omega)}^k(0)$. Thus the paper analyzes a single tight cluster, not general
multi-cluster geometries. This restriction should be stated much earlier, ideally already in the
abstract and introduction, especially because the literature review discusses multi-clustered
configurations and the sentence on p.~3 saying that the earlier computational-resolution-limit
results are generalized to positive sources currently reads more broadly than what is actually
proved here.

\item \textbf{Compare the positive-source lower bounds directly with the general-source lower
bounds from [32].} This should be done either in Section~1.2 or after the lower bounds are stated
in Theorems~2.2 and~2.4 on pp.~8--9. A direct comparison would make the contribution
easier to assess. In one dimension, [32] gives
\[
D_{\mathrm{num}}>\frac{0.81\,e^{-3/2}}{\Omega}
\left(\frac{\sigma}{m_{\min}}\right)^{1/(2n-2)},
\qquad
D_{\mathrm{supp}}>\frac{0.49\,e^{-3/2}}{\Omega}
\left(\frac{\sigma}{m_{\min}}\right)^{1/(2n-1)}.
\]
After rewriting (1.2)--(1.3) in the same normalization, the present paper gives
\[
D_{\mathrm{num}}^{+}>\frac{2^{1+\frac{1}{2n-2}}e^{-1}}{\Omega}
\left(\frac{\sigma}{m_{\min}}\right)^{1/(2n-2)},
\qquad
D_{\mathrm{supp}}^{+}>\frac{2^{1+\frac{1}{2n-1}}e^{-1}}{\Omega}
\left(\frac{\sigma}{m_{\min}}\right)^{1/(2n-1)}.
\]
Thus the exponents are unchanged, but the coefficients improve by the factors
\[
\frac{2^{1+\frac{1}{2n-2}}\sqrt e}{0.81}
\qquad\text{and}\qquad
\frac{2^{1+\frac{1}{2n-1}}\sqrt e}{0.49},
\]
respectively. Numerically, these gains range from about $4.1$ to $5.8$ for number detection and
from about $6.7$ to $8.5$ for support recovery, depending on $n$.

\item \textbf{Supplement the main one-dimensional thresholds by their SRF/SNR form.} The
paper already uses this interpretation later in Sections~5.2 and~6.2, where the phase-transition
discussion is given in the $(\log\mathrm{SRF},\log\mathrm{SNR})$ plane with slopes $2n-2$ and
$2n-1$. It would help the reader to bring this reformulation forward to Section~1.2, around
(1.2)--(1.3), and/or immediately after Theorems~2.1 and~2.3, where the one-dimensional
thresholds are first stated. I do not suggest replacing the present formulas. Rather, for
comparison with earlier super-resolution results, it would be helpful to supplement them with the
equivalent statements that number detection requires
\[
\mathrm{SNR}\gtrsim (C\,\mathrm{SRF})^{2n-2},
\]
while stable support recovery requires
\[
\mathrm{SNR}\gtrsim (C\,\mathrm{SRF})^{2n-1}.
\]
This is the scale-invariant content of the bounds, and it would be useful to make it explicit
already when the one-dimensional thresholds first appear.

\item \textbf{Sharpen the literature review on p.~4.} In the paragraph beginning ``To the best of
our knowledge, the theoretical possibility of super-resolution of positive sources was first
considered in [15] ...'', I recommend adding one sentence explaining the relation to classical
Prony-type identifiability, namely that $n$ point sources are recoverable from $2n$ noiseless
moments.

\item \textbf{Describe the lower-bound proof more accurately relative to [32].} This comment
applies in particular to the sentence in Section~7 beginning ``Our new technique provides a
way ...'' and to the proof discussion in Section~8. I suggest moderating this language and saying
instead that the proof follows the [32] framework -- nullspace construction for an
underdetermined Vandermonde system, moment cancellation, coefficient control, and bounds on the
remainder of the power-series expansion of $F[\gamma]$ -- with the new step being the analysis
that enforces positivity. This would be more accurate.

\item \textbf{Add a practical corollary after (2.4).} On p.~9, after the localization estimate
(2.4), it would be useful to record the direct consequence of inequalities (2.3) and (2.4):
if
\[
d_{\min}:=\min_{p\neq q}|y_p-y_q|,
\]
then
\[
|\hat y_j-y_j|< c_n\,d_{\min}
\]
with \(c_n<0.08\) for every \(n\ge2\). This is a nice practical consequence of the theorem and
should be stated explicitly.

\item \textbf{Address the following concrete presentation issues.}
On p.~7, and consistently throughout the paper, replace the current nonstandard norm notation by the standard notation
$\|\cdot\|$ rather than $||\cdot||$.
Also on p.~7, replace bare references such as ``[30, Theorem ...]'' by explicit
hyperlinks or cross-references where appropriate in the electronic version.
Finally, where the main thresholds are stated on pp.~3, 5, 7, and 8, and in the
discussion around (2.3)--(2.4) on p.~9, supplement the existing
$(\Omega,\sigma,m_{\min})$ formulations by explicit SRF/SNR reformulations.
\end{enumerate}

\end{document}
